%---------------------------------------------------------
% Preliminaries: Set up your own details in this file!
%----------------------------------------------------------

% Don't forget to remove the ()s in ALL of these "personalization" lines.

\title{Development of a comprehensive learning management system designed for
computer science}

\author{Bailin He}
\dept{Computer Science}   % E.g., Physics, Computer Science,
\deptOrSchool{School}
\degree{Computer Science}  % E.g., Science, Arts, ...

\submissionMonth{July}	    % OR WHATEVER MONTH YOU ACTUALLY SUBMIT IN
\submissionYear{2018}
\copyrightYear{2018}		    % Probably the same as submissionYear.

% Use a "~" after the "r." of "Dr." so that TeX doesn't think you have
% ended a sentence (at which point it gives extra space).
\supervisor{Dr. James Diamond}

% Remove the '%' from the next line and fill in the name if desired.
%\cosupervisor{(Dr.~Your Other Supervisor)}

\headOrDirector{Dr. Darcy Benoit}
% If the head or director is an ``acting'' head or director, uncomment
% the next line (i.e., delete the '%'):
% \justActing

% You will have to ask around to find out the name of the person
% to put here... it changes from year to year.
\honoursCommittee{Dr. Matthew Lukeman} % To end of August

%-------------------------------------------------------------------------

% This outputs the title page, the approval page and the copyright page.
\firstThreePages

%-------------------------------------------------------------------------
% Now write your acknowledgements (if any).
% If you wish to acknowledge no-one, delete or comment-out the
% next few lines.

\Acknowledgments
I would like to express my greatest gratitude to my parents,
for none of this could happen without the
support from you, and your endless amounts of love to me is something for which
I can never be thankful enough.

\medskip

I would like to thank my supervisor, Dr.~James Diamond for your
guidance on this project, as well as everything you taught me over these four
years I studied at Acadia University.
It is you who enlightens me to be a better computer scientist.

\medskip

I would like to thank my beloved girlfriend, Yixin Yang,
for being so patient, supportive, and loving to me during the whole process
of this project, 
and for you being the closest person to me, listening to me, sharing with me.
I am so lucky to have you be in every day of my life.

\medskip

I would like to thank all my friends and family, for being around with me all
the time in my life, it is you who shaped me to the person
I am today.

%-------------------------------------------------------------------------

% This outputs the table of contents, lists of figures, tables, ...

\tocAndSuch

%-------------------------------------------------------------------------

\prefacesection{Abstract}

This thesis presents a learning management system (LMS) written in Python using
the Django web framework. This system is designed specifically for computer
science instructors and students to ease the process of submitting and,
more importantly, the process of grading assignments. 
The most important feature in this system is the built-in code
testing module for programming assignments, which brings the system capabilities
to automatically build and run all students'
submitted solutions and provide informative test results for students and
markers.
The system also offers other features like syntax highlighting, Markdown input
and \TeX\ notation input for mathematical equation rendering for
markers and instructors to comment on the students' assignments.


%-------------------------------------------------------------------------

% Don't mess with this line!
\afterpreface
